\documentclass[]{saumya-resume}
\usepackage{fancyhdr}
\usepackage{tfrupee}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\lastupdated

\namesection{Saumya}{Jain}{ \urlstyle{same}\href{https://saumyajain.org/}{saumyajain.org }| 470.363.1437\\
\href{mailto:samjain0913@gatech.edu}{samjain0913@gatech.edu} |
\href{https://github.com/sjain0913}{github.com/sjain0913} |
\href{https://www.linkedin.com/in/sj0913/}{linkedin.com/in/sj0913}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

\section{Summary}
{\bf Hands-on experience in full stack}\\
{\bf development, app development,}\\
{\bf data analytics, and AI/ML. I am }\\
{\bf looking for internship roles for 2021!}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Georgia Institute of}
\subsection{Technology}
\vskip 0.05in
\descript{BS in Computer Science}
\descript{ GPA: 3.61 / 4.0}
\location{Aug 2018 - Dec 2021 | Atlanta, GA}
\vskip 0.05in
{\bf Faculty Honors:} Summer'19,\\
Spring'20 (4.0 GPA)\\
{\bf Dean's List:} 2018-2020 (3.0 + GPA) \\
{\bf GT Lorraine} Summer Program in Summer'19 in Metz, France
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Computer Org \& Progamming \\
Data Structures \& Algs \\
Intro to Artificial Intelligence \\
Combinatorics \\
Objects \& Design \\
Multivariable Calculus \\
Linear Algebra \\
Probability \& Statistics\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{}   Python \textbullet{} React.js \textbullet{} Node.js \\
Express.js \textbullet{} C \textbullet{} Dart \textbullet{} R \textbullet{} Kotlin \textbullet{} \\ 
HTML/CSS \textbullet{} Flutter \textbullet{} React Native \\
Flask \textbullet{} Assembly
\sectionsep

\subsection{Expertise}
Full Stack Development (MERN) \textbullet{} \\
Data Analytics (Python/R) \textbullet{} \\
App Development (Native/Cross Platform) \textbullet{} Intro AI \\
\sectionsep

\subsection{Technologies}
MongoDB \textbullet{} Google Cloud \textbullet{} \LaTeX \\
Android Studio \textbullet{} Unity \textbullet{} Blender \\
RStudio \textbullet{} Clickteam Fusion \\
\sectionsep

\subsection{Languages}
English (native) \\
Hindi (native) \\
French (intermediate)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Boston Scientific}
\descript{|  Software Development Intern }
\location{Jun 2020 - Aug 2020}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Engineered \emph{Twilight} mobile application using Java \& Kotlin for secure control of spinal cord implant for 10,000+ patients.
\item Developed Mobile Device Management system for patients through custom launcher with private widgets and notification filtering.
\item Implemented group video calling software for use by 1000+ employees.
\item Pioneered face detection software using the Firebase ML Toolkit to check employee compliance with mask policies during COVID-19.
\item All development through CI/CD practices with GitLab and extensive unit/integration testing and profiling.
\end{tightemize}
\sectionsep

\runsubsection{Science \& Tech Ministry of India}
\descript{|  Data Analyst \& Researcher}
\location{Jul 2017 – Aug 2017}
\begin{tightemize}
\item Published 10 page report on the outlook of mental health in India by 2030.
\item Scraped data using Python. Visualized and modeled using R \& Python libraries (NumPy, SciPy, Pandas, Matplotlib).
\item Offered data driven solutions to improve access to resources and healthcare.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Booze App}
\descript{| Cross Platform App Development | \href{https://boozeapp.org/}{boozeapp.org}}
\location{Apr 2020 – Current}
\begin{tightemize}
\item Constructing Flutter app for live measure of user's Alcohol Concentration.
\item Support for over 30,000 products through built API deployed on Google Cloud. Used Google Firebase for application tools.
\item Implementing features for emergencies, taxi booking, friend tracking, etc.
\item Pitched to Georgia Tech as solution for student alcohol consumption risks.
\end{tightemize}
\sectionsep

\runsubsection{Booze API}
\descript{| Full Stack API (MERN) | \href{https://boozeapp.org/api}{boozeapp.org/api}}
\location{Apr 2020 – Current}
\begin{tightemize}
\item Deployed REST API with alcohol concentrations of 30,000+ products.
\item Built scalable backend using MongoDB, Express.js, Node.js and Google Cloud. Scraped 200,000+ entries using Python libraries, pushed through Postman.
\item Engineered system for upto 1000 concurrent connections through Atlas.
\item Working on React.js frontend with user authorization and licensing.
\end{tightemize}
\sectionsep

\runsubsection{AllGather - GT Project Team}
\descript{| App Development \& Data Analytics}
\location{Jan 2019 – Jun 2019}
\begin{tightemize}
\item Spearheaded development of app and collected over 5,000 miles of highway data in China, deployed to Google Cloud for analysis.
\item Implemented modules to collect 700+ phone readings per minute using Kotlin.
\item Used Python to detect data anomalies, forwarded to authorities for road repair.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Involvement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Involvement} 
{\bf Chi Psi Fraternity:} Brother, Wellness Chair, Academic Chair \\
\vskip 0.05in
{\bf FilmMakers@GT:} Produced 5 films for festivals, involved in direction, acting, writing\\
\vskip 0.05in
{\bf Gurukool School:} Taught upto 8th grade at underprivileged school, raised funds for new computers (\rupee 200,000 = \$2600).
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
